Deep Learning

### 2015-01-12 deepreview.tex
added more image-to-caption examples

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\caption{Example of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced from~\citet{Vinyals-et-al-arxiv2014}.
}
\end{minipage}
}
\label{fig:caption-generation}
\end{figure}

>>>>

\begin{figure}[ht]
\fbox{
\begin{minipage}{\textwidth}
\centerline{\includegraphics[width=\linewidth]{caption-generation-Vinyals-et-al.png}}
\centerline{\includegraphics[width=0.49\linewidth]{Examples_im2txt_001.png}
\includegraphics[width=0.49\linewidth]{Examples_im2txt_002.png}}
\caption{Examples of captions generated by a recurrent network taking
as extra input the representation extracted by a deep convolutional
net from an image, with the whole system trained to ``translate''
images into captions. Reproduced with permission from~\citet{Vinyals-et-al-arxiv2014}.
}
\end{minipage}
}
\label{fig:caption-generation}
\end{figure}
